Sparsity Weak Lensing $3$-D Density Map Reconstruction: Reducing the line of sight smearing

### 2020-12-05 doc/paper_ms_method_HSCY1/ms.tex
detection as function of threshold and lambda 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd35.pdf 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd40.pdf 	new file:   doc/paper_ms_method_HSCY1/detfalse_threshold_NFW_lbd50.pdf separate tex file into sub tex files 	modified:   doc/paper_ms_method_HSCY1/ms.tex 	new file:   doc/paper_ms_method_HSCY1/massmap_sim.tex 	new file:   doc/paper_ms_method_HSCY1/sparse_NFW_results.tex 	new file:   doc/paper_ms_method_HSCY1/sparse_PointMass_results.tex peak histograms(normalized) and fit noises' peak histograms to Gaussia

This paper is organized as follows.
In Section \ref{sec:Method}, we propose the new method for $3$-D density map
reconstruction.
In Section \ref{sec:Test}, we test the novel algorithm on HSC-like simulations.
In Section \ref{sec:Sum}, we summarize and discuss the future development of
the method.

\section{Methodology}
\label{sec:Method}

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
 \caption{The source galaxies are binned into $10$ redshift bins according to
     their Machine Learning and photo-Z (MLZ) best photo-$z$ estimation. The
     blue histogram is the normalized number distribution of the best photo-$z$
     estimation. The vertical dashed lines are the boundaries of the redshift
     bins.  The galaxies are equal-number binned.
        } \label{fig_bestpz}
\end{figure}

We first review the lensing process in section \ref{subsec:method-delta2shear}.
Then, we introduce the dictionary used to model the foreground density maps in
section \ref{subsec:method-dictionary}.

Subsequently, in section \ref{subsec:method-Systematics}, we discuss several
systematic effects from observations which include photo-$z$ uncertainty
(section \ref{subsec:method-photoz}), smoothing (section
\ref{subsec:method-smoothing}), masking(section \ref{subsec:method-msknoise}),
and pixelization (section \ref{subsec:method-pixel}).

Finally, we solve the mass reconstruction problem in section
\ref{subsec:method-reconstruction} using the adaptive lasso algorithm
\citep{AdaLASSO-Zou2006} optimized with the FISTA algorithm
\citep{FISTA-Beck2009}.

\subsection{Lensing}
\label{subsec:method-delta2shear}

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
 \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.
        }\label{fig_pdfpz}
\end{figure}

@@

As shown in \citet{massMap-KS1993}, the shear field is related to the kappa
field at the same redshift plane via
\begin{equation}\label{eq-kappa2gamma}
\gamma_L(\vec{\theta},z_s) = \int  d^2 \theta' D(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s),
\end{equation}
where
\begin{equation}
D(\vec{\theta})=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2}.
\end{equation}
Here we denote the physical shear distortion field as $\gamma_L$ and we note
that the final observed shear measurements are influenced by systematic errors
from observations. The systematic errors will be discussed in Section
\ref{subsec:method-Systematics}.

@@

\subsection{Dictionary}
\label{subsec:method-dictionary}

\begin{figure*}[!t]
\centering
\subfigure[lasso]{\includezraphics{delta-3-7-pz-nn-lasso.pdf}}
\subfigure[adaptive lasso]{\includezraphics{delta-3-7-pz-nn-alasso.pdf}}
\caption{The density map reconstructions with the lasso (left) and the adaptive
        lasso (right) algorithms. The input density map is from a NFW halo with
        mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso
        reconstruction smears the density field along the line of sight
        direction (vertical direction in the plots).  The vertical direction is
        the line of sight direction, and the lower boundaries and upper
        boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively. Noises
        on galaxy shape measurements are neglected in this simulation.
        } \label{fig_lassoVsadaLasso}
\end{figure*}

@@

The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the
transverse plane are shown in Figure \ref{fig_atoms2D}. The $1$-D slices of the
profiles are demonstrated in Figure \ref{fig_atoms1D}. Note that these profiles
are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The
smoothing operation is discussed in Section \ref{subsec:method-smoothing}, and
the pixelization operation is discussed in Section \ref{subsec:method-pixel}.

\subsection{Systematics}
\label{subsec:method-Systematics}

The observed shear measurements are deviated from the physical shear prediction
due to the systematic errors from observations. The influence of systematics is
carefully studied and incorporated into the forward modeling in this section.

\subsubsection{Photo-$z$ Uncertainty}
\label{subsec:method-photoz}

@@

\subsubsection{Smoothing}
\label{subsec:method-smoothing}

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{shapeMeasurementError-HSCY1.pdf}
 \caption{The histograms of the HSC-like shape measurement error (including
         both from shape noise and from photon noise) on the first component of
         shear ($g_1$) for galaxies (blue lines) and smoothed pixels (orange
         lines). The solid steps are the sampled histograms, and the dashed
         lines are the normalized Gaussian distributions that have the same
         standard deviations as the corresponding histograms.
        }
 \label{fig_noiseHistogram}
\end{figure}

@@

As we will discuss in Section \ref{subsec:method-pixel}, the smoothed shear
field is pixelized into equally spaced grids. We note that another widely used
scheme is to average the shear measurements in each pixel.  Such a scenario is
equivalent to resampling the shear field smoothed with a $3$-D top-hat kernel
with the same scale as the pixels.

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{noise_std_map_pix.pdf}
 \caption{The standard deviation pixel map of the HSC-like shape measurement error for the fifth source galaxy bin
        ($0.69 \leq z < 0.80 $).
        } \label{fig_noistdmap}
\end{figure}

\subsubsection{Masking}
\label{subsec:method-msknoise}

\begin{figure*}[!t]
 \centering
 \includegraphics[width=1.0\textwidth]{peak_scatters_f3-1.pdf}
 \caption{The left panel shows the stacked $2$-D distribution of the deviations
     of detected peak positions from the centers of the corresponding input
     halos. The $x$-axis is for the deviated distance in the transverse plane,
     and the $y$-axis is for the deviation of the redshift. For each
     simulation, the positive peak inside the dashed black box with the
     minimal offset (in the pixel unit) from the input halo's position is
     taken as a true detection. The right panel focuses on the deviation of
     detected peaks in the line of sight direction. The $x$-axis is the input
     halo redshifts, and the $y$-axis is the redshift of the detected peak. The
     `$\cross$' denotes the average redshift of detected peaks for each halo
     over different noise realizations, and the error-bars are the
     uncertainties of the average redshifts. The deep gray area is for the
     relative redshift bias less than $0.05$, and the light gray area is for
     the relative redshift bias less than $0.5$. These results in this figure
     are based on the NFW dictionary with $\lambda=3.5$.
     } \label{fig_detoffsets}
\end{figure*}

@@

\subsubsection{Pixelization}
\label{subsec:method-pixel}

\begin{figure*}[!t]
 \centering
 \includegraphics[width=1.0\textwidth]{detfalseRate_f3-1.pdf}
 \includegraphics[width=1.0\textwidth]{detfalseRate_f3-3.pdf}
 \caption{The upper panels show the halo detection rate and the number of false
     peaks per square degree for mass map reconstructed with the NFW atoms. The
     penalization parameter is set to $\lambda=3.5$ for the upper panels.  The
     low panels show the results for $\lambda=5.0$.
        } \label{fig_detFalsRateNFW}
\end{figure*}

@@

\subsection{Density map reconstruction}
\label{subsec:method-reconstruction}

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.5\textwidth]{peak_histograms.pdf}
 \caption{The histograms of detected peak values from all of the simulations.
     The solid lines with different colors are the results of reconstructions
     with the NFW dictionary penalized with different regularization
     parameters: $\lambda=3.5,4.0,5.0$. The dashed lines are the corresponding
     results of reconstructions from pure noise fields.
    }\label{fig_peakHist}
\end{figure}

@@

\section{Tests}
\label{sec:Test}

\begin{figure*}[!t]
\centering
\subfigure[NFW: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
        }
\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=5.0$]{
        \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
        }
\caption{The results of density maps reconstruction with the point mass
    dictionary (left) and the NFW dictionary (right) with $\lambda=3.5$ (upper)
    and $\lambda=5.0$ (lower). The input density map is from a NFW halo with
    mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The
    vertical direction is the line of sight direction, and the lower boundaries
    and upper boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively.
        } \label{fig_NFWvsPM}
\end{figure*}

This section simulates weak-lensing shear fields induced by a group of halos
with various halo masses and redshifts. The shear fields are used to distort
the HSC mock shape catalogs with different realizations of the HSC-like shape
measurement error and photo-$z$ uncertainty (Section \ref{subsec:Sims}).

Then, we test our algorithm using the simulations with different setups of the
regularization parameter. We also compare the results of our algorithm, which
uses the NFW dictionary (Section \ref{subsec:test-nfw}), with the point mass
dictionary (Section \ref{subsec:test-pm}).

The $\Lambda$CDM cosmology used for the simulations is from the best fitting
result of the final full-mission Planck observation of the cosmic microwave
background (CMB) with $H_0=67.4 ~\rm{km~s^{-1} Mpc^{-1}}$ $\Omega_M=0.315$,
$\Omega_\Lambda=0.685$ \citep{cmb-Planck2018-Cosmology}.

\subsection{Simulations}
\label{subsec:Sims}

We sample halos in a two-dimensional redshift-mass plane. The redshift-mass
plane is evenly divided into eight redshift bins and eight mass bins. We
randomly shift the input halo redshifts and halo masses from the bins' centers
by a small amount. The concentration of the NFW halo is set as a function of
the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
\citet{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
\end{equation}
The weak-lensing shear fields of these NFW halos are simulated according to
\citet{haloModel-TJ2003-3pt}. The shear distortions are applied to one hundred
realizations of galaxy catalogs with the HSC-like shape measurement error and
photo-$z$ uncertainty.

The galaxy catalogs are simulated using the HSC S16A shape catalog
\citep{HSC1-catalog}.  We use galaxies in a one square degree region at the
center of tract 9347 \citep{HSC1-data}.  The galaxies' positions are randomized
to have a homogeneous distribution statistically in the one-square
degree stamp. We randomly assign its redshift for each galaxy following the
MLZ photo-$z$ probability distribution function from By randomly rotating the
galaxies in the shape catalog, we simulate the HSC-like shape estimation error
with different realizations.  The histogram of the first component of the
HSC-like shape estimation error on galaxy level is shown in Figure
\ref{fig_noiseHistogram}.  The corresponding histogram of the shape error on
the pixel level after smoothing and pixelization is also shown in
\ref{fig_noiseHistogram}, and the standard deviation map of the noise is
demonstrated in Figure \ref{fig_noistdmap}.  \citep{HSC1-photoz}.

\subsection{NFW atoms}
\label{subsec:test-nfw}

\begin{figure*}[!ht]
 \centering
 \includegraphics[width=1.0\textwidth]{detfalseRate_f1-1.pdf}
 \includegraphics[width=1.0\textwidth]{detfalseRate_f1-3.pdf}
 \caption{The upper panels show the halo detection rate and the number of false
     peak per square degree for mass map reconstructed with the point mass
     dictionary. The penalization paramter is set to $\lambda=3.5$ for the
     upper panels.  The lower panels show the results for $\lambda=5.0$.
        }\label{fig_detFalsRatePM}
\end{figure*}

In this subsection, we test the performance of our algorithm with the default
setup that models the matter density field with multi-scale NFW atoms. The
dictionary is constructed with three frames of different NFW comoving scale
radius: $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc.  The
truncation radius (concentration) is set to four times the scale radius for the
atoms in the dictionary.

We test the algorithm with different regularization parameters for the
preliminary lasso estimation which range from $3.5$ to $5.0$. The
regularization parameter for the adaptive lasso is set to
$\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\tau+1}$.
Here, we note that both the preliminary lasso estimation and the final adaptive
estimation select the modes with signal to noise ratios (SNRs) greater than
$\lambda_{\rm{ls}}$ in each iteration. While the final adaptive lasso
estimation further enhances the growth of the modes with preliminary
estimations greater than $\lambda_{\rm{ls}}$.

This paper does not go beyond the resolution limit defined by the Gaussian
smoothing kernel with the scale: $1.\arcmin 5$ and the pixel scale
that equals $1\arcmin$. We smooth the reconstructed density with the same
Gaussian kernel in each lens redshift plane.

We detect the peaks on the density map after the reconstruction. The stacked
$2$-D histogram, from all of the simulations, for the offsets of the detected
peak positions from the input halos' positions is shown in the left panel of
Figure \ref{fig_detoffsets}.

For each simulation, we find the positive peak closest to the input position
(in the pixel unit), and if the closest peak lay inside the region denoted with
the dashed box in the left panel of Figure \ref{fig_detoffsets}, we take it as
a true peak detection of the input halo. Other detected peaks, which include both
positive and negative peaks, are taken as false peaks. The right
panel of Figure \ref{fig_detoffsets} shows the average redshift of true
detections for each halo. The estimated redshifts are lower than the true
redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.

Figure \ref{fig_detFalsRateNFW} shows the detection rate (left panels) and the
number of false peaks per square degree (right panel) for each simulated halo.
The figure include results of different penalization parameters: $\lambda=3.5$
(upper panel) and $\lambda=5.0$ (lower panel).  We find that with the increase
of the penalization parameter, the detection rate decreases. On the other hand,
the number of false peaks also decreases.

Figure \ref{fig_peakHist} shows the histograms, which are normalized by the
number of simulations, for all detected peaks with different penalization
parameters. We also plot the corresponding histograms for peaks detected from
pure noise fields for comparison. From the left panels of Figure
\ref{fig_NFWvsPM}, which show the $3$-D density maps reconstructed with
different penalization parameters for a halo with $M_{200}=10^{15.02}
~h^{-1}M_{\odot}$ at redshift $0.164$ , we also find that the number of false
peaks significantly decreases as the penalization parameter increases.

\subsection{Point mass atoms}
\label{subsec:test-pm}

\begin{figure*}
 \includegraphics[width=1.0\textwidth]{detfalse_threshold.pdf}
 \caption{The left panel and the middle panel show the halo detection rates
     with different input masses and redshifts. The detections are performed on
     the mass maps reconstructed with $\lambda=5.0$, and the detection
     thresholds are set to $1.5\sigma$ and $3.0\sigma$ of the peak's standard
     deviation of the noise field, respectively. The right panel shows the
     numbers of false peaks per square degree as a function of selection
     thresholds. The corresponding false peaks per square degree for thresholds
     of $1.5\sigma$ and $3.0\sigma$ are about $0.022~\rm{deg}^{-2}$ and
     $0.004~\rm{deg}^{-2}$.
    }\label{fig_detfalse_threshold}
\end{figure*}

In this subsection, we show the results for the setup, which substitutes the
default NFW dictionary with the point mass dictionary, to compare with the
default setup.  The regularization parameter for the preliminary lasso is set
to $3.5$ and $5.0$.  Inspired by \citet{structureAdaLasso-Pramanik2020}, which
propose to incorporate external group information into different adaptive lasso
penalization weights by setting the penalization weights for projection
coefficients in the same group to the average of the adaptive weights in this
group, we smooth the preliminary lasso estimation in each lens redshift bin
with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc. The smoothed
preliminary lasso estimation is denoted as $\hat{x}^{\rm{ls}}_{\rm{sm}}$, and
the penalization weights are set to $1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\tau$.
The regularization parameter for the adaptive lasso is set to
$\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.

As we have done on the NFW dictionary's reconstruction, we smooth the
reconstructed density maps with the Gaussian kernel (scale radius equals
$1.\arcmin 5$) in each lens redshift plane.

Figure \ref{fig_detFalsRatePM} shows the detection rate (left panels) and the
number of false peaks per square degree (right panel) for each setup of halo
mass and redshift.
This figure includes results of different penalization parameters:
$\lambda=3.5$ (upper panel) and $\lambda=5.0$ (lower panel). The right panels
of Figure \ref{fig_NFWvsPM} show the $3$-D density maps reconstructed with
different penalization parameters for a halo with $M_{200}=10^{15.02}
~h^{-1}M_{\odot}$ at redshift $0.164$.
Comparing with the results of the NFW dictionary, we find that the number of
false peaks in the mass map reconstructed with the point mass dictionary is
much larger than the NFW dictionary.

As demonstrated in the right panels of Figure \ref{fig_NFWvsPM}, the mass
reconstructions with the point mass dictionary tend to assign masses to
several different redshift bins in the neighboring region of the halo center.
While the NFW dictionary produces consistent mass reconstructions.
Since the NFW atoms' profiles are more consistent with the mass profiles of the
input halos than the profile of a point mass, there are less false structures
reconstructed with the NFW dictionary.

\section{Summary}
\label{sec:Sum}

>>>>

This paper is organized as follows.
In Section \ref{sec_Method}, we propose the new method for $3$-D density map
reconstruction.
In Section \ref{sec_Test}, we test the novel algorithm on HSC-like simulations.
In Section \ref{sec_Sum}, we summarize and discuss the future development of
the method.

\section{Methodology}
\label{sec_Method}

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
 \caption{The source galaxies are binned into $10$ redshift bins according to
     their Machine Learning and photo-Z (MLZ) best photo-$z$ estimation. The
     blue histogram is the normalized number distribution of the best photo-$z$
     estimation. The vertical dashed lines are the boundaries of the redshift
     bins.  The galaxies are equal-number binned.
        } \label{fig_bestpz}
\end{figure}

We first review the lensing process in Section \ref{subsec_method_delta2shear}.
Then, we introduce the dictionary used to model the foreground density maps in
Section \ref{subsec_method_dictionary}.

Subsequently, in Section \ref{subsec_method_Systematics}, we discuss several
systematic effects from observations which include photo-$z$ uncertainty
(Section \ref{subsec_method_photoz}), smoothing (Section
\ref{subsec_method_smoothing}), masking(Section \ref{subsec_method_msknoise}),
and pixelization (Section \ref{subsec_method_pixel}).

Finally, we solve the mass reconstruction problem in Section
\ref{subsec_method_reconstruction} using the adaptive lasso algorithm
\citep{AdaLASSO-Zou2006} optimized with the FISTA algorithm
\citep{FISTA-Beck2009}.

\subsection{Lensing}
\label{subsec_method_delta2shear}

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{mlz-poz.pdf}
 \caption{The average PDF of MLZ photo-$z$ error for $10$ source redshift bins.
        }\label{fig_pdfpz}
\end{figure}

@@

As shown in \citet{massMap-KS1993}, the shear field is related to the kappa
field at the same redshift plane via
\begin{equation}\label{eq-kappa2gamma}
\gamma_L(\vec{\theta},z_s) = \int  d^2 \theta' D(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s),
\end{equation}
where
\begin{equation}
D(\vec{\theta})=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2}.
\end{equation}
Here we denote the physical shear distortion field as $\gamma_L$ and we note
that the final observed shear measurements are influenced by systematic errors
from observations. The systematic errors will be discussed in Section
\ref{subsec_method_Systematics}.

@@

\subsection{Dictionary}
\label{subsec_method_dictionary}

@@

The $2$-D profiles of the point mass atom and the multi-scale NFW atoms on the
transverse plane are shown in Figure \ref{fig_atoms2D}. The $1$-D slices of the
profiles are demonstrated in Figure \ref{fig_atoms1D}. Note that these profiles
are smoothed with a Gaussian kernel and pixelized into evenly spaced grids. The
smoothing operation is discussed in Section \ref{subsec_method_smoothing}, and
the pixelization operation is discussed in Section \ref{subsec_method_pixel}.

\subsection{Systematics}
\label{subsec_method_Systematics}

The observed shear measurements are deviated from the physical shear prediction
due to the systematic errors from observations. The influence of systematics is
carefully studied and incorporated into the forward modeling in this Section.

\subsubsection{Photo-$z$ Uncertainty}
\label{subsec_method_photoz}

\begin{figure*}
\centering
\subfigure[lasso]{\includezraphics{delta-3-7-pz-nn-lasso.pdf}}
\subfigure[adaptive lasso]{\includezraphics{delta-3-7-pz-nn-alasso.pdf}}
\caption{The density map reconstructions with the lasso (left) and the adaptive
        lasso (right) algorithms. The input density map is from a NFW halo with
        mass $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$. The lasso
        reconstruction smears the density field along the line of sight
        direction (vertical direction in the plots).  The vertical direction is
        the line of sight direction, and the lower boundaries and upper
        boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively. Noises
        on galaxy shape measurements are neglected in this simulation.
        } \label{fig_lassoVsadaLasso}
\end{figure*}

@@

\subsubsection{Smoothing}
\label{subsec_method_smoothing}

@@

As we will discuss in Section \ref{subsec_method_pixel}, the smoothed shear
field is pixelized into equally spaced grids. We note that another widely used
scheme is to average the shear measurements in each pixel.  Such a scenario is
equivalent to resampling the shear field smoothed with a $3$-D top-hat kernel
with the same scale as the pixels.

\subsubsection{Masking}
\label{subsec_method_msknoise}

@@

\subsubsection{Pixelization}
\label{subsec_method_pixel}

@@

\subsection{Density map reconstruction}
\label{subsec_method_reconstruction}

@@

@@

\section{Tests}
\label{sec_Test}

This Section simulates weak-lensing shear fields induced by a group of NFW
halos with various halo masses and redshifts. The shear fields are used to
distort the HSC mock shape catalogs with different realizations of the HSC-like
shape measurement errors and photo-$z$ uncertainties (Section \ref{subsec_Sims}).

Then, we test our algorithm using the simulations with different setups of the
regularization parameter. We also compare the results of our algorithm, which
uses the NFW dictionary (Section \ref{subsec_test-nfw}), with the point mass
dictionary (Section \ref{subsec_test-pm}).

\subsection{Simulations}
\label{subsec_Sims}
\input{massmap_sim.tex}

\subsection{NFW atoms}
\label{subsec_test-nfw}
\input{sparse_NFW_results.tex}

\subsection{Point mass atoms}
\label{subsec_test-pm}
\input{sparse_PointMass_results.tex}

\begin{figure*}
\centering
\subfigure[NFW: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
        }
\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=5.0$]{
        \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
        }
\caption{The results of density maps reconstruction with the point mass
    dictionary (left) and the NFW dictionary (right) with $\lambda=3.5$ (upper)
    and $\lambda=5.0$ (lower). The input density map is from a NFW halo with
    mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The
    vertical direction is the line of sight direction, and the lower boundaries
    and upper boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively.
        } \label{fig_NFWvsPM}
\end{figure*}

\section{Summary}
\label{sec_Sum}
